Enhancement of SDR in Thessaloniki

### 2024-03-05 GHI_enh_04_investigate.tex
Commit 2024-03-05 19:12

@@

\begin{verbatim}
2024-03-05 09:51:07.3 athan@tyler GHI_enh_04_investigate.R 1.319722 mins
\end{verbatim}

>>>>

\begin{verbatim}
Warning: The dot-dot notation (`..count..`) was deprecated in ggplot2 3.4.0.
i Please use `after_stat(count)` instead.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

@@

\begin{verbatim}
2024-03-05 16:54:52.8 athan@tyler GHI_enh_04_investigate.R 1.097087 mins
\end{verbatim}
